---
title: "analysis of processed FCM data from SP10 entrapment assay"
output: html_notebook
editor_options: 
  chunk_output_type: inline
---

```{r}
# clear environment
rm(list = ls())
library(tidyverse)
library(cowplot)
```

I first need to collect all the data from the cluster pipeline.
* currently only delta6 on DSM is really well clustered
* delta6 on LB is OK in x100
* W23 data is incorrect

I will first collect it all and then fikter out the good data.
```{r, include=FALSE}
# get all the file names to collect
files <- list.files("../data/entrap_data/output/", recursive = TRUE, full.names = TRUE)
d <- data.frame()

for (f in files){
      #get the day from file name
      day <- parse_number(gsub(".*day","",f))
      tmp <- read_csv(f)
      tmp$day <- day
      d <- rbind(d, tmp)
}
rm (tmp)

```

Compare x10 dilution to x100 dilution. Should be 1:1.  
```{r}
d%>%
   select("day","host","phage","rep","media","time","dilution", "spore.ml","veg.ml")%>%
   gather(key="pop", value = "cell.ml", c("veg.ml", "spore.ml"))%>%
   spread(dilution,cell.ml)%>%
   ggplot(aes(x=x10, y=x100))+
      geom_abline(intercept = 0,slope = 1, color="grey")+
      geom_point(aes(color=phage),shape=21)+
      theme_cowplot()+
   scale_y_log10()+scale_x_log10()+
   facet_wrap(host~media)


```

Overall for delta 6 the numbers ar close to 1:1.  
```{r}
filter(d, host=="delta6")%>%
      filter(media=="DSM")%>%
      ggplot(aes(x=phage, y=spore.ml))+
            geom_point(aes(shape=rep, color=time))+
            facet_grid(day~dilution)+
   theme_cowplot()
            
```

```{r}
filter(d, host=="delta6")%>%
      filter(media=="DSM")%>%
      # filter(veg>1000)%>%
      ggplot(aes(x=phage, y=veg.ml))+
            geom_jitter(aes(shape=rep, color=time), width=.2, height = 0)+
            scale_y_log10()+
            facet_grid(day~dilution)+
   theme_cowplot()
            
```

```{r}
filter(d, host=="delta6")%>%
      filter(media=="LB")%>%
      filter(dilution=="x100")%>%
      ggplot(aes(x=phage, y=spore.ml))+
            geom_jitter(aes(shape=rep, color=time), width=.2, height = 0)+
            scale_y_log10()+
            facet_grid(day~dilution)

filter(d, host=="delta6")%>%
      filter(media=="LB")%>%
      filter(dilution=="x100")%>%
      ggplot(aes(x=phage, y=veg.ml))+
            geom_jitter(aes(shape=rep, color=time), width=.2, height = 0)+
            scale_y_log10()+
            facet_grid(day~dilution)+
   theme_cowplot()
            
```

```{r}
# filter(d, host=="delta6")%>%
#       filter(media=="DSM")%>%
#    filter(time=="T4")%>%
#    gather(key="pop", value = "cell.ml", c("veg.ml", "spore.ml"))%>%
#       # filter(veg>1000)%>%
#       ggplot(aes(x=interaction(rep,phage), y=log10(cell.ml)))+
#             geom_bar(aes(fill=pop), stat = "identity")+
#             # scale_y_log10()+
#             facet_grid(dilution~day)+
#    coord_flip()
            
```

# looking at change across days
```{r}

d%>%
   filter(host=="delta6")%>%
   filter(media=="DSM")%>%
   filter(time=="T4")%>%
   gather(key="pop", value = "cell.ml", c("veg.ml", "spore.ml"))%>%
   ggplot(aes(x=day, y=cell.ml))+
      geom_line(aes(color=pop, linetype=rep))+
      scale_y_log10()+
      facet_grid(dilution~phage)+
   theme_cowplot()
```

#summary stats

I will start with delta6 on DSM using the data from x10 dilution and summarizing over biologival replicates.  
```{r}

d%>%
   filter(media=="DSM")%>%
   filter(host=="delta6")%>%
   filter(dilution=="x10")%>%
   gather(key="pop", value = "cell.ml", c("veg.ml", "spore.ml"))%>%
   group_by(phage,pop, day, time)%>%
   summarise(sd=sd(cell.ml),cell.ml=mean(cell.ml) ) ->
d.sum

d.sum
   
```

```{r}
d.sum$lower <- d.sum$cell.ml-d.sum$sd
d.sum$upper <- d.sum$cell.ml+d.sum$sd

d.sum%>%
   ggplot(aes(x=day, y=cell.ml,color=phage))+
      geom_line()+
      geom_pointrange(aes(ymin=lower, ymax=upper), shape=21, fill="white")+
      scale_y_log10()+
      facet_grid(time~pop)+
   scale_x_continuous(breaks = c(1,2))+
   theme_cowplot()
```

